\documentclass[a4,9pt]{beamer}
\usetheme{Berlin}
\usepackage{multicol}
\usepackage{xcolor}
\usepackage{graphicx}
\linespread{1.35}
\usepackage{amsmath}
\usepackage{color}
\usepackage{tikz}
\usetikzlibrary{arrows,automata}

\begin{document}

\begin{frame}
\section*{Minimization of Finite Automata}
\begin{flushright}
 \texttt{CHAPTER TWO} \hspace*{0.1cm}\textbf{$|$} \hspace*{0.1cm} \textbf{26}\hspace*{0.1cm}
\end{flushright}
\vspace*{1cm}
constructed by human beings. As such, finding useful and accurate information on the
Net requires a certain amount of skill as well as access to a variety of research and
retrieval engines.

REFERENCES
December ,J.(1994). Challenges for a webbed society. Computer-mediated Communication Magazine,
J(8).[online].Availabe:http://www.december.com/cmc/mag/1994/nov/websoc. html.
Diamond, E, Bates, S.(1995).The ancient history of the Internet .American Heritage,46. 34-45
Jackson, M.(1997).Assessing the structure of communication on the World Wide Web. journal of
Computer Mediated communication, 3(1).[online]. Availabe: http://www.ascuse.org/jcmc/vol3/
issuel/jackson.html.
March,G.(1988).Hypermedia and learning: Freedom and chaos.Educational Technology,28(11),
8-12.
Nelson,T,H.(1967).getting it out of our system,In G.Schechter(Ed),Information retrival:A
critical review(pp.191-210).Washington, DC: Thompsone.
Sterling, B.(1993).A short bistory of the Internet by Bruce Sterling.[online].Available: http://w3
.aces.uiuc.edu/AIM/Scale/nethistory.html.
Under wired.(199).history of the /internet.[online].Available: http://www.underwired.com/report/
uw.css.
\end{frame}
\end{document}